Measurement of a dwarf galaxy rotational velocity from its Lyman-alpha line emission

### 2016-02-01 paper/letter.tex
observational limits on HI mass

The metallicity is $\sim Z_{\odot}/24$ \cite{Izotov04} as derived from optical
spectroscopy. The observed flux for the Lyman alpha line is $\sim
8.1\times 10^{-14}$ erg cm$^{-2}$ s$^{-1}$ \AA$^{-1}$ \cite{Thuan97}
and a Equivalent Width of $70$\AA.

@@

\begin{equation}
M_{T} = \frac{V^{2}D}{G} = 4.32\times10^{5}
\left(\frac{V}{\mathrm{km\ s}^{-1}}\right)^2\left(\frac{D}{\mathrm{kpc}}\right) M_{\odot}
\end{equation}
\end{document}

>>>>

The receeding velocity is $7785\pm 50$km s$^{-1}$, which translates
into a distance of $106.6$ Mpc (Hubble constant 73 Mpc km$^{-1}$
s$^{1}$)
The metallicity is $\sim Z_{\odot}/24$ \cite{Izotov04} as derived from optical
spectroscopy. The observed flux for the Lyman alpha line is $\sim
8.1\times 10^{-14}$ erg cm$^{-2}$ s$^{-1}$ \AA$^{-1}$ \cite{Thuan97}
and a Equivalent Width of $70$\AA, with the emission comming from a
region with approximate diameter ?. There is an upper limit for the
integrated flux of $<0.10$ Jy km s$^{-1}$, which translates into a
upper limit for the HI mass of $M<2.65\times 10^{8}$ M$_{\odot}$
\cite{pustilnikmartin07}.

@@

\begin{equation}
M_{T} = \frac{V^{2}D}{G} = 2.16\times10^{5}
\left(\frac{V}{\mathrm{km\ s}^{-1}}\right)^2\left(\frac{D}{\mathrm{kpc}}\right) M_{\odot}
\end{equation}
\end{document}
